Exploring the structure of the bound proton with Deeply Virtual Compton Scattering

### 2019-05-23 eg6-letters/incoherent/incoherent_prl.tex
add updated figure 4 and response to the referees

\begin{figure*}[t!]
\includegraphics[height=4.2cm,trim={0 0 1.59cm 0},clip]{ALU_90_p_vs_Q2_shortscenrario.pdf}
\includegraphics[height=4.2cm,trim={3cm 0 1.6cm 0},clip]{ALU_90_p_vs_x_shortscenrario.pdf}
\includegraphics[height=4.2cm,trim={3cm 0 1.6cm 0},clip]{ALU_90_p_vs_t_shortscenrario.pdf}
\caption{The $Q^{2}$ (left), $x_{B}$ (middle), and $t$ dependencies (right) of
   the fitted $A_{LU}$ at $\phi$~=~90$^{\circ}$ (black squares). The error bars 
   represent the statistical uncertainties, while the gray bands represent the 
   systematic uncertainties. On the middle plot the curves are theoretical 
   calculations from \cite{simonetta_2}. On the right plot the solid (empty) 
   green circles are the HERMES $-A_{LU}$ (a positron beam was used) inclusive 
   measurements for the incoherent (coherent) enriched region 
   \cite{Airapetian:2009cga}; the curves represent theoretical calculations 
   from \cite{simonetta_2}.}
\label{fig:alu90}
\end{figure*}

>>>>

\begin{figure*}[t!]
\includegraphics[height=5.2cm,trim={0 0 0cm 
   0},clip]{ALU_90_p_shortscenrario.pdf}
\caption{The $Q^{2}$ (left), $x_{B}$ (middle), and $t$ dependencies (right) of
   the fitted $A_{LU}$ at $\phi$~=~90$^{\circ}$ (black squares). The error bars 
   represent the statistical uncertainties, while the gray bands represent the 
   systematic uncertainties. On the middle plot the curves are theoretical 
   calculations from \cite{simonetta_2}. On the right plot the solid (empty) 
   green circles are the HERMES $-A_{LU}$ (a positron beam was used) inclusive 
   measurements for the incoherent (coherent) enriched region 
   \cite{Airapetian:2009cga}; the curves represent theoretical calculations 
   from \cite{simonetta_2}.}
\label{fig:alu90}
\end{figure*}
